Circumpolar variations in the chaotic nature of Southern Ocean eddy dynamics

### 2022-04-16 revised_paper/ResponseToReviewers.tex

\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{color}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Brief Article}
\author{The Author}
%\date{}                                           % Activate to display a given date or no date

\begin{document}
%\maketitle

We would like to convey our thanks to both reviewers for the constructive and positive reviews of our paper. 
In the following we have addressed each of the reviewers' comments -- with their comments in blue and our response in plain text.

\section*{Response to Reviewer 1}

{\color{blue} This study uses an ensemble of 50 simulations from an eddy-permitting ocean model to investigate the relative importance of forced (coherent) and intrinsic (chaotic) eddy responses. The simulations use the same wind forcing but differ from each other by adding a stochastic perturbation over 1960. The authors define the forced EKE as the ensemble mean EKE from the 50 simulations, and the chaotic EKE as the difference between each simulation and the ensemble mean. The authors find that the Southern Ocean eddy field is dominated by intrinsic processes instead of forced processes. In addition, the authors identified two timescales on which the wind stress and the forced eddy field are linked.

Overall, the question is important, the approach is creative, the findings are significant, and the presentation is high quality. I think the paper is certainly publishable in JGR. I only have a few minor comments and questions, which I hope the authors can clarify before my recommendation of acceptance.\\}

\noindent Our thanks to the reviewer for their positive assessment. 
We have responded in detail to each of the reviewer's comments below.

\subsection*{\color{blue}Details:}

{\color{blue} 
\begin{description}
\item[ Line 84: ] ``the Southern Ocean", missing words like EKE or eddy field?\\
{\color{black}  We agree and have changed to read ``Southern Ocean EKE'' }

\item[ Lines 140-141:] ``the member's global mean sea level anomaly", is this a single value or a time series? If this is a value, it's more likely to shift each ensemble member's sea surface height with a different value. But it wouldn't affect the sea level anomaly time series at each grid point. \\
{\color{black} This statement refers to a timeseries of the globally averaged sea level anomaly. We have clarified this statement to read:\\
 ``For each ensemble member, and at every time step, the member's global mean sea level anomaly is subtracted at every grid point  \ldots" }

\item[Lines 158-162:] The authors mention that the seasonal EKE variation dominates the statistics. To look at the forced response or the correlation between ensemble-mean EKE and wind stress, they deseasonalize the EKE time series. There is some missing information about how they smooth wind stress, the same as the deseasonalized EKE? Also, maybe some general information about the wind stress can be provided in the method section.\\
{\color{black} Yes, the seasonal cycle is also removed from the wind stress. We have added, on line 189, the caveat that wind stress ``\ldots has been deseasonalised in a similar way to $E_i$ \ldots". }

\item[Lines 176-179:] ``Analogously, the intrinsic variance emerges from the variance, indicating the spread of each member from the ensemble mean"; I feel this sentence is not accurate. Normally the closest meaning of spread is the standard deviation. I would suggest the author rephrase it like this: ``For each time step, the intrinsic variance emerges from the variance of EKE difference between ensemble mean and each member of the 50 simulations.'' \\
{\color{black} Amended as suggested. }

\item[Lines 185-186:] between the EKE (...) AND WHAT? Missing words?\\
{\color{black} We have added ``and its forcing''. }

\item[Line 201:] show $\to$ shows\\
{\color{black} Amended. }

\item[Figure 1:] The ensemble mean EKE pattern is consistent with the mean EKE pattern from satellite altimetry. Since this study focuses more on the EKE variabilities, it would be helpful showing to what extent the averaged EKE anomaly time series (group members and ensemble mean) agree with the EKE anomaly time series from satellite altimetry. Also, please label the longitude, latitude, and the major topographic features. \\
{\color{black}  }

\item[Line 231:] add citations (e.g., Meredith \& Hogg, 2006; Hogg et al., 2015) \\
{\color{black} Added as suggested }

\item[Line 231:] As found in this paper, the significance of the wind-leading lag correlation is affected by the size and location of the research area. To compare with previous studies, such as Meredith \& Hogg (2006), Hogg et al., (2015), doesn't it make more sense to use the same average boxes? \\
{\color{black} This line actually refers to the circumpolar average, and so provides a direct comparison, as the reviewer suggests.  
For the later parts of the paper where we examine sub-domains, we considered replicating the original Meredith \& Hogg (2006) boxes, but we found that the ensemble approach allows us to refine those boxes to be considerably smaller, while still obtaining meaningful results.
We could happily add an extra figure with the larger Meredith \& Hogg (2006) boxes, but considered this to be of marginal value to the reader.}

\item[Figure 2:] Based on the definition of EKE and wind stress, they should always be positive. To be accurate, I would suggest the authors label them clearly. Same comment for time series plots in figure 3 and figure 4. \\
{\color{black} We agree more information is needed here and  have noted in the caption of figure 2 that the timeseries shows ``ensemble mean {\color{red}EKE anomaly} (red) along with wind stress {\color{red}anomaly} \ldots'', where red text has been added. 
The captions for figures 3 and 4 have been similarly clarified.}

\item[Line 239-240:] What's the T value for the 4 months and 30 months peaks? \\
{\color{black}  }

\item[Line 241:] dominanent $\to$ dominant?\\
{\color{black} Corrected, thankyou. }

\item[Line 274:] Southeast $\to$ Southwest\\
{\color{black} Amended. }

\item[Figure 3:] (a) A colorbar could be useful. Also, when you define the 3 boxes, do you use rectangular boxes like (70$^\circ$E-120$^\circ$E, 45$^\circ$S-60$^\circ$S)? The boxes shown in Figure 3(a) are more like irregular polygons. It will be better if the author can describe how those boxes are defined. \\
{\color{black}  }

\item[Line 276:] Do the envelopes in Figures 2(b), 3(d), and 4(d) indicate significant lag correlations? If so, it's not accurate to state "no significant response" here.\\
{\color{black} We agree with the reviewer here and have removed that statement. }

\item[Figure 4:] (a) Same comments as Figure 3 (a). In figure 4(b), the caption of the right axis is missing. \\
{\color{black}  }

\item[Figure 5:] Why is there a small missing longitudinal sector?\\
{\color{black} The small missing sector is a consequence of coarsening onto the larger grid, meaning that periodic fields are poorly mapped onto the circumpolar projection. }

\end{description}
}

\newpage

\section*{Response to Reviewer 2}

{\color{blue} I would like to begin by apologising to the authors for the delay in my review. Unfortunately, it became due at a time where there were multiple demands upon my time and I did a poor job at managing them. I apologise for the delay to the publication process this has caused.

The paper is an interesting and well written look at how variability in the Southern Ocean. It is presented very clearly, despite the complex nature of mesoscale eddy dynamics and the challenges of analysing what I am sure is a very large dataset. The analysis uses some simple statistical metrics to break the variability into a fraction that is due to intrinsic variability and that due to direct forcing from wind stress. The conclusions are well supported by the data and the figures are extremely clear. It is very easy for me to recommend publication as-is.

I have noted a few very minor things below, which the authors may wish to address at the proof stage.\\}

\noindent Our thanks to the reviewer for their suggestions; see the following for our responses.

{\color{blue} 
\begin{description}
\item[line 66;] dynamics, plural or singular? I'm not sure.\\
{\color{black} Singular -- amended to ``dynamic''. }

\item[line 128;] is this spinup forced by DFS5.2 as well?\\
{\color{black} Yes -- we have added that information to the revised manuscript. }

\item[line 139;] daily or day?\\
{\color{black} Altered to ``day''.}

\item[line 158;] is the subsampling achieved by selecting a single mean or by averaging them into monthly equivalents?\\
{\color{black} We don't quite understand the point that the reviewer is getting at here, but have clarified by adding the phrase ``\ldots  through weighted averages". }

\item[line 161;] removing THE mean seasonal cycle\\
{\color{black} Amended as suggested }

\item[line 197;] is the $r$ in Eq. (10) the correlation coefficient at the current lag, rather than at a specific lag?\\
{\color{black} Yes, $r$ is as defined 9 lines earlier. }

\item[line 214;] ensemble member AS thin grey lines\\
{\color{black} Amended as suggested. }

\item[line 241;] dominanent to dominant?\\
{\color{black} Corrected. }

\item[line 372;] a reference would be helpful for anyone unfamiliar with the literature.\\
{\color{black} Reference to Arbic \& Flierl (2004) added. }

\end{description}
}

\end{document}

### 2022-04-16 revised_paper/revised.tex
starting revisions

Another unique feature of the Southern Ocean is that it has a strong eddy field \citep{Fu2010}.
This eddy field has been suggested to be important in the Southern Ocean's response to change.
For example, the eddy saturation hypothesis \citep{Hallberg2006, Meredith-Hogg-2006, Munday2013, Constantinou2019} suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
A similar dynamics, known as eddy compensation, describes the role of eddies in moderating the effect of wind-driven change on the Southern Ocean overturning circulation \citep{Morrison2013a}.
Therefore, the response of mesoscale transient motion in the Southern Ocean is likely important to characterising the dynamics of this region.

The strength of the Southern Ocean eddy field is usually characterised by extracting the kinetic energy of transient motions; referred to by oceanographers as eddy kinetic energy (EKE). 
It is important to highlight that EKE includes all transient motion, not just coherent vortices \citep{Martinez-Moreno2019}, and thus care needs to be taken in interpreting this metric.
Eddy kinetic energy has a complex relationship with the forces that drive the ocean circulation.
\citet{Meredith-Hogg-2006} found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between wind stress forcing variations and EKE anomalies that follow.
\citet{Patara2016}, using a realistic high-resolution ocean model found that EKE does have a lagged response to wind stress anomalies, but that this relationship varies in strength around the Southern Ocean.
Idealised model studies over a wide range of parameter space \citep{Sinha2016} have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
Thus, current knowledge suggests that there is a relationship between wind forcing and the Southern Ocean, but that the nature of this relationship needs to be clarified.

@@

The methodology employed in this study is derived from the probabilistic approach to ocean modelling outlined by \citet{Bessieres2017}.
We use output from the OCCIPUT ensemble of 50 eddy-permitting global ocean--sea ice simulations, based on the ORCA025 implementation \citep[e.g.][]{Barnier2006} of the NEMO modelling system \citep{Madec2012}. 
The model grid has a 1/4$^\circ$ horizontal resolution and 75 geopotential levels. 
The approach involves:
\begin{enumerate}
\item The 50 ensemble members are initialized in 1960 from a single-member 21-year spinup;
\item The ensemble spread is seeded by activating a stochastic perturbation \citep{Brankart-etal-2015} over one year (1960), after which the perturbation is terminated;
\item The 50 ensemble members are integrated from 1960 to 2015, driven by the same realistic atmospheric forcing function based on the ERA-40 and ERA-Interim reanalyses (Drakkar Forcing Set DFS5.2; \citet{Dussin-etal-2016}).
\end{enumerate}
In these simulations the wind stress is computed without ocean current feedbacks, hence ensuring that the same momentum fluxes are applied to all members. 
We focus our analyses on the period 1980-2015, thus yielding an effective spinup duration of 41 years in each member.

\subsection{Estimating geostrophic eddy velocity}
For each ensemble member, the sea surface height, $\eta_i$, is saved as a 5-daily average (where $i$ represents the ensemble member). 
For each ensemble member, the member's global mean sea level anomaly is subtracted from all grid points at every time step to correct for spurious terms introduced by the use of the Boussinesq approximation \citep{Greatbatch1994}. 
The model drift, which is potentially nonlinear, is then corrected for by detrending using a LOWESS filter \citep{Cleveland1979} in combination with a 5th-order spline; full details of this preprocessing may be found in \cite{Close2020}.

@@

The surface eddy kinetic energy for each ensemble member is calculated as 
\begin{linenomath*}
\begin{equation}
E_i = \frac{1}{2}(u_i'^2 + v_i'^2),
\end{equation}
\end{linenomath*}
and subsampled at monthly temporal resolution.
It is notable that $E_i$ contains a large component of seasonal variation which dominates the statistics \citep{Martinez-Moreno2021}.
To look at the forced response, we therefore deseasonalise $E_i$, by removing mean seasonal cycle.
We then proceed to compute ensemble statistics from this deseasonalised EKE.

@@

The eddy kinetic energy can be averaged over the $N$ ensemble members to give the ensemble mean EKE, written as
\begin{linenomath*}
\begin{equation}
\langle E \rangle = \frac{1}{N} \sum_{i=1}^N E_i.
\end{equation}
\end{linenomath*}
The argument can be made that, since each ensemble member is forced with identical atmospheric conditions, the forced EKE response is captured by this ensemble mean quantity.
On the other hand, the intrinsic variability of EKE in each ensemble member is found by taking the difference from the ensemble mean for each member,
\begin{linenomath*}
\begin{equation}
E_i^* = E_i - \langle E \rangle,
\end{equation}
\end{linenomath*}
where $\cdot^*$ is used to indicate departure from the ensemble mean.
With these expressions in hand, we follow \citet{Leroux2018} to define the  time-variance of the ensemble-mean EKE,
\begin{linenomath*}
\begin{equation}
\sigma^2_{\langle E \rangle} = \frac{1}{T} \sum_{t=1}^T \left(\langle E \rangle -  \overline{\langle E \rangle}\right)^2,
\end{equation}
\end{linenomath*}
which represents the variance of the forced eddy response.
Analogously, the intrinsic variance emerges from the variance,
\begin{linenomath*}
\begin{equation}
\epsilon^2(t) = \frac{1}{N} \sum_{i=1}^N E_i^*(t)^2,
\end{equation}
\end{linenomath*}
indicating the spread of each member from the ensemble mean.
The fraction of intrinsic variance is then computed as the ratio of the intrinsic variance to the total variance,
\begin{linenomath*}
\begin{equation}
R_i =  \frac{\overline{\epsilon^2}}{\overline{\epsilon^2} + \sigma^2_{\langle E \rangle}}.
\end{equation}
\end{linenomath*}
When $R_i$ approaches unity, the system is dominated by intrinsic variability, while at the limit  of $R_i \to 0$ the system is solely responding to forced variability induced by atmospheric forcing.

To examine the relationship between the EKE (of either the ensemble mean, or from individual ensemble members) we are guided by previous work which emphasises the role of wind stress in governing the eddy variability at different timescales \citep[e.g.][]{Hogg2015, Sinha2016}.
Thus, we look at the correlation coefficient, $r$, at a range of lags between the wind stress $|\tau|$ (which is identical for all ensemble members) and EKE.
For each correlation we evaluate the statistical significance of the correlation \citep[following, e.g.][]{Santer2000}.
We first calculate the effective sample size, $N_e$, where
\begin{linenomath*}
\begin{equation}
N_e \equiv N \frac{1-r_1 r_2}{1+r_1 r_2},
\end{equation}
\end{linenomath*}
where $N$ is the total number of samples (444 months for this timeseries), $r_1$ is the lag-1 autocorrelation for EKE and $r_2$ is the lag-2 autocorrelation for wind stress.
We use the Students t-test to infer statistical significance (at the 95\%-level) based on this effective sample size, when
\begin{linenomath*}
\begin{equation}
T = \frac{r \sqrt{N_e}}{\sqrt{1-r^2}} > 2.
\end{equation}
\end{linenomath*}
Lagged correlation estimates indicate when this significance test is satisfied.

@@

The intensity of the Southern Ocean eddy field is not uniform.
A snapshot of eddy kinetic energy from the model used here (Fig.~\ref{Fig:1}a) show the occurrence of strong eddies which appear in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
The same patterns are evident in the ensemble and temporal mean of the EKE ($\overline{\langle E \rangle}$; Fig.~\ref{Fig:1}b), although the signal of individual eddies is no longer apparent.
The strongest band of EKE approximately follows the path of the Antarctic Circumpolar Current, and EKE is weak south of 60$^\circ$S.
The patterns of EKE in this model broadly match the regional variations of EKE observed from satellite altimetry, albeit at slightly lower intensity, as expected in an eddy-permitting model \citep[e.g.][]{Kiss2020}.

@@

For each of the 50 members of the OCCIPUT ensemble we take the EKE averaged over the entire Southern Ocean (40$^\circ$-60$^\circ$S), and plot the deseasonalised EKE anomalies from each ensemble member in thin grey lines in Fig.~\ref{Fig:2}(a). 
This plot highlights the considerable spread in EKE, even when averaged over the full circumpolar belt; in other words, there is a significant component of chaotic (intrinsic) variability in the Southern Ocean eddy field.
Nonetheless, when averaged over all ensemble members (red line in Fig.~\ref{Fig:2}a) the existence of a coherent (forced) component of eddy variability is revealed.
Averaged over this wide region the fraction, $R_i$, of intrinsic variance is 0.82, confirming the visual impression that intrinsic processes dominate the variability in the eddy field averaged over the basin.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure2}
\caption{Eddy kinetic energy statistics over the Southern Ocean (40$^\circ$S--60$^\circ$S). (a) Spatially averaged deseasonalised EKE anomaly (relative to climatology) for individual ensemble members (grey) and the ensemble mean (red) along with wind stress (black); and (b) Time-lagged correlation between wind stress and EKE for the ensemble mean (red) and individual ensemble  members (grey) -- with two individual ensemble members highlighted in magenta and orange.}
\label{Fig:2}
\end{center}
\end{figure}

Although Southern Ocean EKE variability is strongly intrinsic, there remains a component of forced variability (red line in Fig.~\ref{Fig:2}a).
Previous studies have inferred that there is a strong contribution of wind stress forcing upon EKE, and we therefore compare the forced variability with the variations in wind stress averaged over the same circumpolar belt (black line in Fig.~\ref{Fig:2}a).
This comparison suggests a relationship in which wind stress leads variations in EKE, consistent with previously published results.
However, the time-lagged correlations between wind stress and EKE implies that this relationship is complex. 
The intrinsically variable nature of Southern Ocean eddies means that for some ensemble members, there is no meaningful correlation between wind stress and eddies (grey lines in Fig~\ref{Fig:2}b).
On the other hand, ensemble member 5 (magenta line) has a clear (and significant; $T = 5.5$) correlation with a 4-month lag, while member 25 (orange line) is weakly correlated at 6 months, and significantly correlated ($T = 4.2$) at a 24-month lag.
These isolated examples highlight the differing behaviour of each ensemble member. 
The ensemble mean (red line in Fig~\ref{Fig:2}b) includes a significant correlation at $\sim$4 months and a second significant peak at $\sim$30 months.
Thus, two distinct timescales of response of the Southern Ocean eddy field to wind stress are present in this model, overprinted by a dominanent and complex influence of chaotic variability.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure3}
\caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean. (a) Map showing ensemble mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southeast Indian Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southwest Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (e) Regional analysis of the South Atlantic Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black. The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
\label{Fig:3}
\end{center}
\end{figure}

@@

In the Southeast Pacific Ocean (red box in Fig.~\ref{Fig:3}a) the situation clearly differs.
Here, the intrinsic variance fraction is larger than in the Southeast Indian Ocean ($R_i=0.78$) and the timescale of the variability is much longer; there is no significant response to wind stress variations which occur at sub-annual scales (Fig.~\ref{Fig:3}d).
The maximum values in the lag correlation occur over a broad band from 9-24 months in this region, without a single clear peak.
Thus, this region varies slowly and consistently to interannual variations in wind stress, albeit with a strong chaotic component.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure4}
\caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean. (a) Map showing ensemble mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Central South Pacific Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southeast Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (e) Regional analysis of the Southwest Indian  Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black. The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
\label{Fig:4}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure7}
\caption{(a) The intrinsic variance fraction, $R_i$, averaged onto a  4$^\circ \times$4$^\circ$ grid and with a 12-month rolling mean; (b) amplitude of variability due to forced processes and (c) amplitude of variability due to intrinsic processes. }
\label{Fig:6}
\end{center}
\end{figure}

>>>>

Another unique feature of the Southern Ocean is that it has a strong eddy field \citep{Fu2010}.
This eddy field has been suggested to be important in the Southern Ocean's response to change.
For example, the eddy saturation hypothesis \citep{Hallberg2006, Meredith-Hogg-2006, Munday2013, Constantinou2019} suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
A similar dynamic, known as eddy compensation, describes the role of eddies in moderating the effect of wind-driven change on the Southern Ocean overturning circulation \citep{Morrison2013a}.
Therefore, the response of mesoscale transient motion in the Southern Ocean is likely important to characterising the dynamics of this region.

The strength of the Southern Ocean eddy field is usually characterised by extracting the kinetic energy of transient motions; referred to by oceanographers as eddy kinetic energy (EKE). 
It is important to highlight that EKE includes all transient motion, not just coherent vortices \citep{Martinez-Moreno2019}, and thus care needs to be taken in interpreting this metric.
Eddy kinetic energy has a complex relationship with the forces that drive the ocean circulation.
\citet{Meredith-Hogg-2006} found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between wind stress forcing variations and EKE anomalies that follow.
\citet{Patara2016}, using a realistic high-resolution ocean model found that EKE does have a lagged response to wind stress anomalies, but that this relationship varies in strength around the Southern Ocean.
Idealised model studies over a wide range of parameter space \citep{Sinha2016} have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
Thus, current knowledge suggests that there is a relationship between wind forcing and Southern Ocean EKE, but that the nature of this relationship needs to be clarified.

@@

The methodology employed in this study is derived from the probabilistic approach to ocean modelling outlined by \citet{Bessieres2017}.
We use output from the OCCIPUT ensemble of 50 eddy-permitting global ocean--sea ice simulations, based on the ORCA025 implementation \citep[e.g.][]{Barnier2006} of the NEMO modelling system \citep{Madec2012}. 
The model grid has a 1/4$^\circ$ horizontal resolution and 75 geopotential levels. 
The approach involves:
\begin{enumerate}
\item The 50 ensemble members are initialized in 1960 from a single-member 21-year spinup using the Drakkar Forcing Set DFS5.2 \citep{Dussin-etal-2016};
\item The ensemble spread is seeded by activating a stochastic perturbation \citep{Brankart-etal-2015} over one year (1960), after which the perturbation is terminated;
\item The 50 ensemble members are integrated from 1960 to 2015, driven by the same realistic atmospheric forcing function based on the ERA-40 and ERA-Interim reanalyses (Drakkar Forcing Set DFS5.2; \citet{Dussin-etal-2016}).
\end{enumerate}
In these simulations the wind stress is computed without ocean current feedbacks, hence ensuring that the same momentum fluxes are applied to all members. 
We focus our analyses on the period 1980-2015, thus yielding an effective spinup duration of 41 years in each member.

\subsection{Estimating geostrophic eddy velocity}
For each ensemble member, the sea surface height, $\eta_i$, is saved as a 5-day average (where $i$ represents the ensemble member). 
For each ensemble member, and at every time step, the member's global mean sea level anomaly is subtracted at every grid point to correct for spurious terms introduced by the use of the Boussinesq approximation \citep{Greatbatch1994}. 
The model drift, which is potentially nonlinear, is then corrected for by detrending using a LOWESS filter \citep{Cleveland1979} in combination with a 5th-order spline; full details of this preprocessing may be found in \cite{Close2020}.

@@

The surface eddy kinetic energy for each ensemble member is calculated as 
\begin{linenomath*}
\begin{equation}
E_i = \frac{1}{2}(u_i'^2 + v_i'^2),
\end{equation}
\end{linenomath*}
and subsampled at monthly temporal resolution through weighted averages.
It is notable that $E_i$ contains a large component of seasonal variation which dominates the statistics \citep{Martinez-Moreno2022}.
To look at the forced response, we therefore deseasonalise $E_i$, by removing the mean seasonal cycle.
We then proceed to compute ensemble statistics from this deseasonalised EKE.

@@

The eddy kinetic energy can be averaged over the $N$ ensemble members to give the ensemble mean EKE, written as
\begin{linenomath*}
\begin{equation}
\langle E \rangle = \frac{1}{N} \sum_{i=1}^N E_i.
\end{equation}
\end{linenomath*}
The argument can be made that, since each ensemble member is forced with identical atmospheric conditions, the forced EKE response is captured by this ensemble mean quantity.
On the other hand, the intrinsic variability of EKE in each ensemble member is found by taking the difference from the ensemble mean for each member,
\begin{linenomath*}
\begin{equation}
E_i^* = E_i - \langle E \rangle,
\end{equation}
\end{linenomath*}
where $\cdot^*$ is used to indicate departure from the ensemble mean.
With these expressions in hand, we follow \citet{Leroux2018} to define the  time-variance of the ensemble-mean EKE,
\begin{linenomath*}
\begin{equation}
\sigma^2_{\langle E \rangle} = \frac{1}{T} \sum_{t=1}^T \left(\langle E \rangle -  \overline{\langle E \rangle}\right)^2,
\end{equation}
\end{linenomath*}
which represents the variance of the forced eddy response.
For each time step, the intrinsic variance emerges from the variance of the EKE difference between ensemble mean and each member of the 50 simulations,
\begin{linenomath*}
\begin{equation}
\epsilon^2(t) = \frac{1}{N} \sum_{i=1}^N E_i^*(t)^2.
\end{equation}
\end{linenomath*}
The fraction of intrinsic variance is then computed as the ratio of the intrinsic variance to the total variance,
\begin{linenomath*}
\begin{equation}
R_i =  \frac{\overline{\epsilon^2}}{\overline{\epsilon^2} + \sigma^2_{\langle E \rangle}}.
\end{equation}
\end{linenomath*}
When $R_i$ approaches unity, the system is dominated by intrinsic variability, while at the limit  of $R_i \to 0$ the system is solely responding to forced variability induced by atmospheric forcing.

To examine the relationship between the EKE (of either the ensemble mean, or from individual ensemble members) and its forcing, we are guided by previous work which emphasises the role of wind stress in governing the eddy variability at different timescales \citep[e.g.][]{Hogg2015, Sinha2016}.
Thus, we look at the correlation coefficient, $r$, at a range of lags between the wind stress $|\tau|$ (which is identical for all ensemble members and has been deseasonalised in a similar way to $E_i$) and EKE.
For each correlation we evaluate the statistical significance of the correlation \citep[following, e.g.][]{Santer2000}.
We first calculate the effective sample size, $N_e$, where
\begin{linenomath*}
\begin{equation}
N_e \equiv N \frac{1-r_1 r_2}{1+r_1 r_2},
\end{equation}
\end{linenomath*}
where $N$ is the total number of samples (444 months for this timeseries), $r_1$ is the lag-1 autocorrelation for EKE and $r_2$ is the lag-2 autocorrelation for wind stress.
We use the Students t-test to infer statistical significance (at the 95\%-level) based on this effective sample size, when
\begin{linenomath*}
\begin{equation}
T = \frac{r \sqrt{N_e}}{\sqrt{1-r^2}} > 2.
\end{equation}
\end{linenomath*}
Lagged correlation estimates indicate when this significance test is satisfied.

@@

The intensity of the Southern Ocean eddy field is not uniform.
A snapshot of eddy kinetic energy from the model used here (Fig.~\ref{Fig:1}a) shows the occurrence of strong eddies which appear in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
The same patterns are evident in the ensemble and temporal mean of the EKE ($\overline{\langle E \rangle}$; Fig.~\ref{Fig:1}b), although the signal of individual eddies is no longer apparent.
The strongest band of EKE approximately follows the path of the Antarctic Circumpolar Current, and EKE is weak south of 60$^\circ$S.
The patterns of EKE in this model broadly match the regional variations of EKE observed from satellite altimetry, albeit at slightly lower intensity, as expected in an eddy-permitting model \citep[e.g.][]{Kiss2020}.

@@

For each of the 50 members of the OCCIPUT ensemble we take the EKE averaged over the entire Southern Ocean (40$^\circ$-60$^\circ$S), and plot the deseasonalised EKE anomalies from each ensemble member as thin grey lines in Fig.~\ref{Fig:2}(a). 
This plot highlights the considerable spread in EKE, even when averaged over the full circumpolar belt; in other words, there is a significant component of chaotic (intrinsic) variability in the Southern Ocean eddy field.
Nonetheless, when averaged over all ensemble members (red line in Fig.~\ref{Fig:2}a) the existence of a coherent (forced) component of eddy variability is revealed.
Averaged over this wide region the fraction, $R_i$, of intrinsic variance is 0.82, confirming the visual impression that intrinsic processes dominate the variability in the eddy field averaged over the basin.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure2}
\caption{Eddy kinetic energy statistics over the Southern Ocean (40$^\circ$S--60$^\circ$S). (a) Spatially averaged deseasonalised EKE anomaly (relative to climatology) for individual ensemble members (grey) and the ensemble mean EKE anomaly (red) along with wind stress anomaly (black); and (b) Time-lagged correlation between wind stress and EKE for the ensemble mean (red) and individual ensemble  members (grey) -- with two individual ensemble members highlighted in magenta and orange.}
\label{Fig:2}
\end{center}
\end{figure}

Although Southern Ocean EKE variability is strongly intrinsic, there remains a component of forced variability (red line in Fig.~\ref{Fig:2}a).
Previous studies have inferred that there is a strong contribution of wind stress forcing upon EKE, and we therefore compare the forced variability with the variations in wind stress averaged over the same circumpolar belt (black line in Fig.~\ref{Fig:2}a).
This comparison suggests a relationship in which wind stress leads variations in EKE, consistent with previously published results \citep{Meredith-Hogg-2006,Hogg2015}.
However, the time-lagged correlations between wind stress and EKE implies that this relationship is complex. 
The intrinsically variable nature of Southern Ocean eddies means that for some ensemble members, there is no meaningful correlation between wind stress and eddies (grey lines in Fig~\ref{Fig:2}b).
On the other hand, ensemble member 5 (magenta line) has a clear (and significant; $T = 5.5$) correlation with a 4-month lag, while member 25 (orange line) is weakly correlated at 6 months, and significantly correlated ($T = 4.2$) at a 24-month lag.
These isolated examples highlight the differing behaviour of each ensemble member. 
The ensemble mean (red line in Fig~\ref{Fig:2}b) includes a significant correlation at $\sim$4 months and a second significant peak at $\sim$30 months.
Thus, two distinct timescales of response of the Southern Ocean eddy field to wind stress are present in this model, overprinted by a dominant and complex influence of chaotic variability.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure3}
\caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean. (a) Map showing ensemble mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southeast Indian Ocean showing ensemble mean EKE anomaly in cyan, individual ensemble members EKE anomaly in grey and local wind stress anomaly averaged over the region in black; (c) Lagged correlation of ensemble mean EKE anomaly with wind stress anomaly in each of the three regions; (d) Regional analysis of the Southwest Pacific Ocean showing ensemble mean EKE anomaly in red, individual ensemble members EKE anomaly in grey and local wind stress anomaly averaged over the region in black; and (e) Regional analysis of the South Atlantic Ocean showing ensemble mean EKE anomaly in orange, individual ensemble members EKE anomaly in grey and local wind stress averaged anomaly over the region in black. The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
\label{Fig:3}
\end{center}
\end{figure}

@@

In the Southwest Pacific Ocean (red box in Fig.~\ref{Fig:3}a) the situation clearly differs.
Here, the intrinsic variance fraction is larger than in the Southeast Indian Ocean ($R_i=0.78$) and the timescale of the variability is much longer (Fig.~\ref{Fig:3}d).
The maximum values in the lag correlation occur over a broad band from 9-24 months in this region, without a single clear peak.
Thus, this region varies slowly and consistently to interannual variations in wind stress, albeit with a strong chaotic component.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure4}
\caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean. (a) Map showing ensemble mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Central South Pacific Ocean showing ensemble mean EKE anomaly in cyan, individual ensemble members EKE anomaly in grey and local wind stress anomaly averaged over the region in black; (c) Lagged correlation of ensemble mean EKE anomaly with wind stress anomaly in each of the three regions; (d) Regional analysis of the Southeast Pacific Ocean showing ensemble mean EKE anomaly in red, individual ensemble members EKE anomaly in grey and local wind stress anomaly averaged over the region in black; and (e) Regional analysis of the Southwest Indian  Ocean showing ensemble mean EKE anomaly in orange, individual ensemble members EKE anomaly in grey and local wind stress anomaly averaged over the region in black. The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
\label{Fig:4}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure7}
\caption{(a) The interannual intrinsic variance fraction, $R_i$, averaged onto a  4$^\circ \times$4$^\circ$ grid and with a 12-month rolling mean; (b) amplitude of interannual variability due to forced processes and (c) amplitude of interannual EKE variability due to intrinsic processes.
 }
\label{Fig:6}
\end{center}
\end{figure}
